Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-03-10 paper.tex
First subsection of introduction

@@

>>>>

\begin{document}

@@

\section{Training Data for MIR}\label{sec:introduction}

Central to the task of content-based Music Information Retrieval is the curation of ground-truth data for tasks of interest (e.g. timestamped chord labels for automatic chord estimation, beat positions for beat tracking, prominent melody time series for melody extraction, etc.).
The quantity and quality of this ground-truth is often instrumental in the success of MIR systems which utilize it as training data.
Unfortunately, creating appropriate labels for a recording of a given song by hand often requires person-hours on the order of the length of the song.
This often arguably makes the available training data a bottleneck to success for a given content-based MIR task.

It has previously been observed that MIDI files, when time-aligned to corresponding audio recordings, can be used to infer ground-truth information about a given song \cite{ewert2012towards, turetsky2003ground}.
This is due to the fact that a MIDI files can be viewed simplistically as a timed sequence of note annotations or a piano roll.
It is much more straightforward to estimate, e.g., beat locations, chord labels, and the predominant melody from these representations than one which was derived from an audio signal.
Unsurprisingly, a handful of tools have been developed for inferring this information from MIDI files \cite{eerola2004mir,mckay2006jsymbolic,cuthbert2010music21,raffel2014pretty_midi}.

In \cite{halevy2009unreasonable}, it is argued that some of the biggest successes in machine learning are thanks to the fact that ``...a large training set of the input-output behavior that we seek to automate is available to us in the wild.''
The main motivation behind this project is that this crucial availability of data holds true for MIDI files - through a large-scale web scrape, we obtained 250,000 unique MIDI files, which is orders of magnitude larger than the datasets typically used for MIR research.
We believe this proliferation of data is largely caused to two factors: First, that karaoke files are typically distributed as MIDI data and that karaoke is wildly popular, and second, that transcribing popular music as MIDI files was a common pastime for hobbyist musicians in the nineties.
